---
title: "solo_cp_change_point_detection_with_simulated_data"
author: "Lorenzo Cappello"
date: "April 10, 2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Adaptive_preferential_sampling_with_simulated_data}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(solocp)
```

We sample some data

```{r}

set.seed(123)

  n <- 271
  sigma <- 0.1
  change.points <- c(31,61,91,121,151,181,211,241)
  true.change.points <- change.points
  change.points <- c(1,change.points,n+1)
  level <- c(0, 1, 0, 1, 0,1,0,1,0)
  level <- level - level[1]
  meanvec<-rep(level,diff(change.points))
  y <-c()
  for (i in meanvec){ y<- c(y,rnorm(1,i,sigma))}
  x <- seq(1,n)/n

```


We plot the data along with the true test signal (red)
```{r}
fun <- stepfun(change.points,c(0,level,0))
plot(y)
lines(fun(seq(1,n)),col="red",lwd=2)
```

We now apply the solocp algorithm. solocp_single computes the marginal inclusion probability.
subset_changepoints removes consecutive change points (it corresponds to point 2-4 in Algorithm 1 in the manuscript)

Here we assume to know the standard deviation (sigma). Otherwise it is needs to be given as an input.

Note, we are using the input default parameters (q, tau2, tau2.spike,tau2.slab). If not they need to be specified in solocp_single (see below)
```{r}
solo <- solocp_single(y,sigma)
cp <- subset_changepoints(solo$ratio,del=5)
```

Plot the results
```{r}
plot(y)
abline(v=cp,lwd=2,col="red")
```
Now we use solo.cp using our own input parameter

```{r}
q=0.1
tau2=2/n
tau2.slab=n
tau2.spike=1/n
solo1 <- solocp_single(y,sigma,q=q,tau2=tau2,tau2.spike=tau2.spike,tau2.slab = tau2.slab)
cp1 <- subset_changepoints(solo1$ratio,del=5)
```

And plot again the results 

```{r}
plot(y)
abline(v=cp1,lwd=2,col="red")
```

